**Density Dependence**

### 2023-03-09 Rmd/report mac.Rmd
Added kobe plots to report.R and report mac.rmd

if ("try-error"%in%is(dropboxdir))
  dropboxdir="~/Dropbox/DDMSE"
```

```{r}
mystk     <- "mac"; mystkname <- "Northeast Atlantic mackerel"; mylatin <- "Scombrus scomber"
# mystk     <- "whb"; mystkname <- "Blue whiting";                mylatin <- "Micromesistius poutassou" 
maxyear <- 2050

load(file=file.path(dropboxdir,paste0("data/om/",mystk,"matPar.RData")))
```

```{r}
# ------------------------------------------------------------------------------
# Operating model
# ------------------------------------------------------------------------------
figuresdir <- file.path(dropboxdir, "results", mystk, "figures")
tablesdir  <- file.path(dropboxdir, "results", mystk, "tables")
```

@@

The OMs were also projected for the estimates of different estimates $F_{MSY}$, with stochasticty in the recruitment deviates. This allows the impact of misspecification of density dependence to be evaluated, i.e. if $F_{MSY}$ is underestimated then yield will be less than MSY, while if $F_{MSY}$ is overestimated yield will be lost due to overfishing. Stochastic projections of the four Operating Models for the four estimates of $F_{MSY}$ are shown in **Figures 16-19**. **Figure 20** summarizes the yields and SSBs obtained for each Operating Model under the correct and mis-specified form of density dependence.

@@

$W_a = {\overline{W_a}} {(B/B_{MSY})^{{\beta}_a}$

@@

Misspecification of Fmsy, i.e. using an Fmsy from one scenario and applying it to a different scenario has only limited impacts on the overall outcomes in terms of recruitment, biomass or yield. In the plot below, the scenarios for density dependence are shown in the columns and the Fmsy's are shown as the colours. For example a valid combination is the Base case with the red curves (Fmsy=0.33) or the M scenario with the green curve. Overall the misspecification does not results in noticeable differences.

@@

As a chech, we assessed the outcomes of the equilibrium curves from simulating over a wide F range, with the equilibrium values (points) in 2050 from the forward projections at different values of Fmsy (colours). The points fall on the equilibrium curve, thereby confirming the consistency between the two approaches.

@@

**Figure 20** summarizes the yields and SSBs obtained for each Operating Model under the correct and misspecified form of density dependence and the associated reference points.

>>>>

if ("try-error"%in%is(dropboxdir))
  dropboxdir="~/Dropbox/DDMSE"

mystk     <- "mac"; mystkname <- "Northeast Atlantic mackerel"; mylatin <- "Scombrus scomber"
# mystk     <- "whb"; mystkname <- "Blue whiting";                mylatin <- "Micromesistius poutassou" 
maxyear <- 2050

load(file=file.path(dropboxdir,paste0("data/om/",mystk,"matPar.RData")))

# ------------------------------------------------------------------------------
# Operating model
# ------------------------------------------------------------------------------
figuresdir <- file.path(dropboxdir, "results", mystk, "figures")
tablesdir  <- file.path(dropboxdir, "results", mystk, "tables")
```

@@

The OMs were also projected for the estimates of different estimates $F_{MSY}$, with stochasticty in the recruitment deviates. This allows the impact of misspecification of density dependence to be evaluated, i.e. if $F_{MSY}$ is underestimated then yield will be less than MSY, while if $F_{MSY}$ is overestimated yield will be lost due to overfishing. Stochastic projections of the four Operating Models for the four estimates of $F_{MSY}$ are shown in **Figures 16-19**. **Figures 20 and 21** summarizes the yields and SSBs obtained for each Operating Model under the correct and mis-specified form of density dependence.

@@

@@

Misspecification of Fmsy, i.e. using an Fmsy from one scenario and applying it to a different scenario has only limited impacts on the overall outcomes in terms of recruitment, biomass or yield. In the plot below, the scenarios for density dependence are shown in the columns and the Fmsy's are shown as the colours. For example a valid combination is the Base case with the red curves (Fmsy=0.33) or the M scenario with the green curve. Overall the misspecification does not results in noticeable differences in catch although they do have difference for biomass.

@@

For the four scenarios, we plotted the Kobe phase plot for 2050 with the associated density functions for B/Bmsy and Catch/MSY. The results confirm the results that equilibrium catch is not really affected by the DD assumptions of the Fmsy applied, but that biomass is sensitive to the assumptions.

```{r, echo=FALSE, out.width = "300px", fig.align="center", message=FALSE, warning=FALSE, cache=FALSE}

fig_nums(
  name    = "kobe", level = 1, display = FALSE,
  caption = "Kobe plot for 2050 for base case (no DD) for all $F_{MSY}$'s (red is from the right scenario). Topleft: base, topright: M, bottomleft: MM, bottomright: MMM")

knitr::include_graphics(path=
                    c(file.path(figuresdir,paste("05",mystk,"kobe base.jpg",sep="_")),
                      file.path(figuresdir,paste("05",mystk,"kobe M.jpg",sep="_")),
                      file.path(figuresdir,paste("05",mystk,"kobe MM.jpg",sep="_")),
                      file.path(figuresdir,paste("05",mystk,"kobe MMM.jpg",sep="_"))
                      )
                    )

*`r fig_nums("kobe")`*

Finally, as a check, we assessed the outcomes of the equilibrium curves from simulating over a wide F range, with the equilibrium values (points) in 2050 from the forward projections at different values of Fmsy (colours). The points fall on the equilibrium curve, thereby confirming the consistency between the two approaches.

@@

**Figure 20** summarizes the yields and SSBs obtained for each Operating Model under the correct and misspecified form of density dependence and the associated reference points, and **Figure 21** shows the Kobe plots of the final 2050 distributions of biomass and yield.
